---
title: "RMarkdown Lab"
author: "Emily Rukstales"
date: "3/3/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```


# Introduction  
#### Here we will be making tables and plots with the ChemData dataset.

# Load Libraries  

```{r LoadLibraries}
library(tidyverse)
library(here)
library(kableExtra)
library(cowplot)
library(calecopal)
```


# Load Data  
#### Using the ChemData from Week 4  

```{r LoadData}
ChemData <- read_csv(here("Week_6", "Data", "chemicaldata_maunalua.csv"))
```


# Create a table  
#### Make a table of all the variables for each site  
  
Calculate variable means for each site
```{r Means}
ChemData_summary <- ChemData %>% # store summary statistics as object
  group_by(Site) %>% # calculate statistics for each site
  summarise(mean_temp = mean(Temp_in, na.rm = TRUE), # calculate means of each variable
            mean_salinity = mean(Salinity, na.rm = TRUE),
            mean_phosphate = mean(Phosphate, na.rm = TRUE),
            mean_silicate = mean(Silicate, na.rm = TRUE),
            mean_NN = mean(NN, na.rm = TRUE),
            mean_pH = mean(pH, na.rm = TRUE),
            mean_TA = mean(TA, na.rm = TRUE),
            mean_pctsgd = mean(percent_sgd, na.rm = TRUE)) %>%
  mutate(mean_temp = round(mean_temp, digits = 2), # round all numbers to 2 decimal places
         mean_salinity = round(mean_salinity, digits = 2),
         mean_phosphate = round(mean_phosphate, digits = 2),
         mean_silicate = round(mean_silicate, digits = 2),
         mean_NN = round(mean_NN, digits = 2),
         mean_pH = round(mean_pH, digits = 2),
         mean_TA = round(mean_TA, digits = 2),
         mean_pctsgd = round(mean_pctsgd, digits = 2)) %>%
  rename("Nitrate + Nitrite (umol/L)" = "mean_NN", #rename variables
         "Percent SGD" = "mean_pctsgd",
         "Total Alkylinity (umol/L)" = "mean_TA",
         "Temperature (C)" = "mean_temp",
         "Phosphate (umol/L)" = "mean_phosphate",
         "Silicate (umol/L)" = "mean_silicate",
         "Salinity" = "mean_salinity",
         "pH" = "mean_pH") %>%
  mutate(Site = ifelse(Site == "BP", "Black Point", "Wailupe")) %>% # change site names inside Site column
    pivot_longer(cols = "Temperature (C)":"Percent SGD", # pivot longer so that all variables are in 1 column
               names_to = "Variables",
               values_to = "Values") %>%
  pivot_wider(names_from = "Site", # pivot wider so there there is 1 column for each site
              values_from = "Values")
```

Create a table showing variable means for each site  
```{r Table}
ChemData_table <- ChemData_summary %>% # use means to create table
  kbl() %>% # create kable
  kable_classic(full_width = F) %>% # classic theme, width does not span entire page
  kable_styling(fixed_thead = T) # fix row sizes

ChemData_table
```

# Create a plot  
#### Make plots of nutrients vs temperature by site  
  
```{r ColorPalette, include = FALSE}
pal <- cal_palette("superbloom3", 2) # use calecopal for plot colors
```
  
Plot nitrate + nitrite vs temperature
```{r NNPlot, fig.show = 'hide'}
NN_plot <- ChemData %>% # create plot of NN vs Temp
  filter(complete.cases(.)) %>% # remove NA's
  mutate(Site = ifelse(Site == "BP", "Black Point", "Wailupe")) %>% # change site names in Site column
  ggplot(aes(x = Temp_in, # temperature on x-axis
             y = NN, # NN on y-axis
             color = Site)) + # color each site
  geom_line() + # make line graph
  theme_bw() +
  theme(legend.position = "none", # remove legend from this plot (will show in second plot)
        plot.margin = margin(10, 20, 20, 20)) + # put a margin around entire plot
  scale_x_continuous(expand = c(0, 0)) + # remove extra white space inside panel
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = pal) + # use color palette for lines
  labs(x = "Temperature (C)", # change axis labels
       y = "Nitrate + Nitrite (umol/L)",
       title = "Nutrients vs. Temperature", # add title
       subtitle = "Nitrate + Nitrite and Phosphates") # add subtitle
```
  
Plot phosphate vs temperature
```{r PhosphatePlot, fig.show = 'hide'}
Phosphate_plot <- ChemData %>% # create plot of phosphate vs temp
  filter(complete.cases(.)) %>% # remove NA's
  mutate(Site = ifelse(Site == "BP", "Black Point", "Wailupe")) %>% # change site names in Site column
  ggplot(aes(x = Temp_in, # temp on x-axis
             y = Phosphate, # phosphate on y-axis
             color = Site)) + # color each site
  geom_line() + # make line graph
  theme_bw() +
  theme(plot.margin = margin(10, 20, 20, 20)) + # put a margin around entire plot
  scale_x_continuous(expand = c(0, 0)) + # remove extra white space inside panel
  scale_y_continuous(expand = c(0, 0)) +
  scale_color_manual(values = pal) + # use color palette for lines
  labs(x = "Temperature (C)", # change axis labels
       y = "Phosphate (umol/L)",
       title = " ",
       subtitle = " ")
```


Stitch nutrients plots together using **{cowplot}** package
```{r Cowplot, fig.width = 13, fig.height = 5, fig.align = "center", fig.path = "../Outputs/"}
plot_grid(NN_plot, Phosphate_plot, # use {cowplot} to join two plots
          labels = c('A', 'B'), # label each plot with a letter
          label_size = 12, # change size of A/B labels
          rel_widths = c(1, 1.25), # adjust widths so that panel dimensions match
          rel_heights = c(1.2, 1), # adjust heights so that panel dimensions match
          label_x = 0.05, # move A/B labels to the right a little
          label_y = 0.9) # move A/B labels down
```



