---
title: "Functions Lab"
author: "Emily Rukstales"
date: "3/24/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```


## Introduction  
In this lab, we will create 2 functions using the Palmer Penguins dataset.  
  
```{r libraries, include = FALSE}
library(tidyverse)
library(here)
library(palmerpenguins)
library(PNWColors)
```
  
  
## Function 1  
Create a function to calculate the ratio of body mass of any other variable.  
  
```{r func1}
body_mass_ratio <- function(data = penguins, x) {
  ratio <- data %>%
    mutate(body_mass_ratio = body_mass_g/{{x}})
  return(ratio)
}
```
  
  
## Examples using Function 1  
Use the body_mass_ratio function to calculate the ratios of body mass to flipper length, and body mass to bill length.  
  
```{r ex1}
body_mass_ratio(x = flipper_length_mm)

body_mass_ratio(x = bill_length_mm)
```
  
  
  
## Function 2  
Create a function to produce line graphs of 2 continuous variables colored by Sex from the Palmer Penguins dataset.
  
```{r func2}
penguinplot <- function(data = penguins, x, y) { 
  pal <- pnw_palette("Winter", 3, type = "discrete")
  
  penguins <- na.omit(penguins)
  
  ggplot(data,
         aes(x = {{x}},
             y = {{y}},
             color = sex)) +
    geom_point() +
    geom_smooth(method = "lm") +
    scale_color_manual("Sex", values = pal) +
    guides(color = guide_legend(override.aes = list(fill = NA))) +
    theme_bw()
}
```
  
  
## Examples using Function 2  
Create a plots of bill depth vs bill length and flipper length vs body mass colored by sex. 
  
```{r ex2, fig.width = 8, fig.height = 5, fig.align = "center"}
penguinplot(x = bill_length_mm, y = bill_depth_mm) +
  labs(x = "Bill length (mm)",
       y = "Bill depth (mm)") +
  ggsave(here("Week_8", "Outputs", "Function2_Plot1.png"))

penguinplot(x = flipper_length_mm, y = body_mass_g) +
  labs(x = "Flipper Length (mm)",
       y = "Body Mass (g)")+
  ggsave(here("Week_8", "Outputs", "Function2_Plot2.png"))
```










